---
title: "Disabling tests using YAML params"
date: "`r Sys.Date()`"
params:
  test: FALSE
---

```{r setup, include = FALSE}
testrmd::init()
testrmd::styles()  # Just temporary--should be automatic
```

### Using YAML to disable tests

By adding `test: FALSE` to your YAML params you can stop test chunks from being evaluated throughout the document. If the parameter is set to `test: TRUE`, test chunks will run as usual.

```
params:
  test: FALSE
```

This test parameter is passed into your chunk options using `eval = params$test`, as shown below.

<!--html_preserve-->
<pre>```{r stopifnot_parameterized, test = TRUE, eval = params$test}
counts <- c(1, 2, 3, 4.5)
stopifnot(
  is.numeric(counts),
  all(counts >= 0),
  isTRUE(all.equal(counts, round(counts)))
)
```</pre><!--/html_preserve-->

### Enabling individual test chunks

To run selected test chunks within the same document, you simply exclude the `eval` option for an individual chunk, or expressly set the chunk option to `eval = TRUE`.

<!--html_preserve-->
<pre>```{r failing_test, test = TRUE, eval = TRUE}
library(assertthat)
assert_that(is.numeric(y))
```</pre><!--/html_preserve-->

```{r failing_test_true, test = TRUE}
library(assertthat)
assert_that(is.numeric(y))
```

